\documentclass[margin,line,11pt]{resume}
\usepackage[colorlinks=true, pdfstartview=FitV, linkcolor=blue, urlcolor=blue]{hyperref}
\usepackage{hyperref}

\usepackage{fontawesome5,url}
\usepackage{eurosym}
\usepackage{libertine}
\usepackage{enumitem}
\usepackage{fontspec}

\usepackage{fancyhdr}

\textheight=10in
\footskip=10pt

\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{0pt} % no line in header area
\fancyfoot[R]{\thepage} % other info in "inner" position of footer line
\pagestyle{fancy}


\setmonofont[Mapping=tex-text,Scale=0.9]{Helvetica} 

\def\myemail{pbarbera@usc.edu}
%\def\myemail{P.Barbera@lse.ac.uk}
\def\myweb{www.pablobarbera.com}
\def\mytwitter{@p\_barbera}

\newcommand{\nl}{\vspace{0.10in}\\}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Pablo Barber\'{a}}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact Information}

    \begin{tabular*}{\textwidth}{ l @{\extracolsep{\fill}} r}
    Dept. of Political Science and International Relations    		& \texttt{\href{mailto:\myemail}{\myemail}} \, \faEnvelope \\
University of Southern California 			& \texttt{\href{\myweb}{\myweb}} \, \faGlobe \\
3518 Trousdale Parkway, VKC 330		& \texttt{\href{http://twitter.com/p_barbera}{\mytwitter}} \, \faTwitter \\
Los Angeles, CA 90089			&  \texttt{\href{http://www.github.com/pablobarbera}{github.com/pablobarbera}} \, \faGithub \\
    \end{tabular*}
    
%    \begin{tabular*}{\textwidth}{ l @{\extracolsep{\fill}} r}
%    Department of Methodology    		& \texttt{\href{mailto:\myemail}{\myemail}} \, \faEnvelope \\
%London School of Economics 			& \texttt{\href{\myweb}{\myweb}} \, \faGlobe \\
%Houghton Street		& \texttt{\href{http://twitter.com/p_barbera}{\mytwitter}} \, \faTwitter \\
%    London, UK WC2A 2AE			&  \texttt{\href{http://www.github.com/pablobarbera}{github.com/pablobarbera}} \, \faGithub \\
%    \end{tabular*}    

%__________________________________________________________________________________________________________________

    \section{\mysidestyle Professional\\Appointments}
    \textbf{Facebook}
    \begin{itemize}
    \item[] Research Scientist, Core Data Science, 2019--
    \end{itemize}
    \vspace{-.15cm}      
    \textbf{University of Southern California}
    \begin{itemize}
    \item[] Associate Professor (with tenure), Political Science and International Relations, 2020--
    \vspace{-.15cm}    
    \item[] Assistant Professor, Political Science and International Relations, 2016--2020
    \vspace{-.15cm}
    \item[] Principal Investigator, Networked Democracy Lab (\textit{netdem.org})
    \end{itemize}    
    \vspace{-.15cm}
    \textbf{London School of Economics and Political Science}
    \begin{itemize}
    \item[] Visiting Fellow, Department of Methodology, 2019--
    \vspace{-.15cm}    
    \item[] Assistant Professor of Computational Social Science, Department of Methodology, 2018--2019
    \end{itemize}
    \vspace{-.30cm}
    \textbf{New York University}
    \begin{itemize}
    \item[] Moore-Sloan Fellow, Center for Data Science, 2015--2016
    \end{itemize}
        
   %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}
\textbf{New York University}
\begin{itemize}
\item[] Ph.D. in Political Science, May 2015
\vspace{-.15cm}
\item[] $\ast$ Committee: Jonathan Nagler, Joshua A. Tucker, Patrick Egan, Neal Beck, Richard Bonneau
\vspace{-.15cm}
\item[] $\ast$  Graduate Research Associate, Social Media and Political Participation (SMaPP) lab
\end{itemize}
\vspace{-.30cm}
\textbf{European University Institute} 
\begin{itemize}
\item[] Master of Research in Political Science, 2010
\end{itemize}
\vspace{-.30cm}
\textbf{Pompeu Fabra University} 
\begin{itemize}
\item[] M.A. in Political and Social Sciences, 2009
\vspace{-.15cm}
\item[] B.A. in Political Science and Administration (with highest honors), 2008 
\end{itemize}

%__________________________________________________________________________________________________________________
    % Publications
    \section{\mysidestyle Peer-Reviewed\\Publications}
\vspace{.15cm}    
\begin{itemize}[leftmargin=5.5mm]

\item[22.] Munzert, S., \textbf{Barber\'{a}, P.}, Guess, A. \& Yang, J. \href{https://academic.oup.com/poq/advance-article/doi/10.1093/poq/nfaa037/6104133}{``Do Online Voter Guides Empower Citizens? Evidence from a Field Experiment with Digital Trace Data,''} forthcoming in \textit{Public Opinion Quarterly}.

\item[21.] 
Fazekas, Z., Popa, S., Schmitt, H., \textbf{Barber\'{a}, P.} \& Theocharis, Y. ``\href{https://ejpr.onlinelibrary.wiley.com/doi/abs/10.1111/1475-6765.12402}{Elite-Public Interaction on Twitter: The EU Issue in the 2014 EP Campaign}'', forthcoming in the \textit{European Journal of Political Research}.

\item[20.] Siegel, A., Nikitin, E., \textbf{Barber\'{a}, P.}, Sterling, J., Pullen, B., Bonneau, R., Nagler, J. \& Tucker, J. ``\href{http://dx.doi.org/10.1561/100.00019045}{Trumping Hate on Twitter? Online Hate Speech and White Nationalist Rhetoric in the 2016 US Election Campaign and its Aftermath}'', \textit{Quarterly Journal of Political Science}, 2021, 16(1): 71--104.

\item[19.] \textbf{Barber\'{a}, P.}, Boydstun, A., Linn, S., Nagler, J., McMahon, R.,  \href{https://www.cambridge.org/core/journals/political-analysis/article/automated-text-classification-of-news-articles-a-practical-guide/10462DB284B1CD80C0FAE796AD786BC6}{``Automated Text Classification of News Articles: A Practical Guide''}, \textit{Political Analysis}, 2021, 29(1): 19--42.

\item[18.] Theocharis, Y., \textbf{Barber\'{a}, P.}, Popa, S., Fazekas, Z. ``\href{https://journals.sagepub.com/doi/full/10.1177/2158244020919447}{The Dynamics of Citizen Incivility Towards Politicians}'', \textit{Sage Open}, 2020, 10(2): 1--15.

\item[17.] \textbf{Barber\'{a}, P.}, Casas. A, Nagler, J., Egan, P., Bonneau, R., Jost, J. \& Tucker, J. \href{https://t.co/6KnjCczsqH}{``Who Leads? Who Follows? Measuring Issue Attention and Agenda Setting by Legislators and the Mass Public Using Social Media Data''}, \textit{American Political Science Review}, 2019, 113(4): 883-901.

\newpage   

\item[16.] Jost, J. T., \textbf{Barber\'{a}, P.}, Bonneau, R., Langer, M., Metzger, M., Nagler, J., Sterling, J. \& Tucker, J. A. \href{http://onlinelibrary.wiley.com/doi/10.1111/pops.12478/full}{``How Social Media Facilitates Political Protest: Information, Motivation, and Social Networks''}, \textit{Political Psychology}, 2018, 39(S1), 85-118.

\item[15.] \textbf{Barber\'{a}, P.} \& Zeitzoff, T. \href{https://academic.oup.com/isq/article/doi/10.1093/isq/sqx047/4430887/The-New-Public-Address-System-Why-Do-World-Leaders}{``The New Public Address System: Why Do World Leaders Adopt Social Media?''}, \textit{International Studies Quarterly}, 2018, 62 (1): 121--130.
    
\item[14.] Bauer, P., \textbf{Barber\'{a}, P.}, Ackerman, K. \& Venetz, A. ``\href{http://link.springer.com/article/10.1007/s11109-016-9368-2}{Is the Left-Right Scale a Valid Measure of Ideology? Investigating the Meaning of `Left' and `Right' and Its Impact on Measurement}'', \textit{Political Behavior}, 2017, 39 (3): 553-583.

\item[13.] Riera, P., G\'{o}mez, R., Mayoral, J.A. \textbf{Barber\'{a}, P.} \& Montero, J.R. ``\href{http://revintsociologia.revistas.csic.es/index.php/revintsociologia/article/view/675/832}{Local Elections in Spain: The Personalization of Voting Behavior}'', \textit{Revista Internacional de Sociolog\'{i}a}, 2017, 75 (2): e062.
\begin{itemize}
\item[] $\ast$ 2017 Best Article Award, given by the Editorial Board of the journal.
\end{itemize}

    
\item[12.] Theocharis, Y., \textbf{Barber\'{a}, P.}, Popa, S., Fazekas, Z. \& Parnet, O. ``\href{http://onlinelibrary.wiley.com/doi/10.1111/jcom.12259/abstract}{A Bad Workman Blames His Tweets. The Consequences of Citizens' Uncivil Twitter Use when Interacting with Party Candidates}'', \textit{Journal of Communication}, 2016, 66 (6): 1007-1031.
\begin{itemize}
\item[] $\ast$ 2016 \href{http://www.apsanet.org/section-18-best-conference-paper-award}{Best Information Technology \& Politics Conference Paper Award}
\end{itemize}

    
\item[11.] Vaccari, C., Valeriani, A., \textbf{Barber\'{a}, P.}, Bonneau, R., Jost, J., Nagler, J., Tucker, J. ``\href{http://sms.sagepub.com/content/2/3/2056305116664221.abstract}{Of echo chambers and contrarian clubs: Exposure to political disagreement among German and Italian users of Twitter}'', \textit{Social Media + Society}, 2016, 2 (3): 1--24.

\item[10.] Riera, P., G\'{o}mez, R., \textbf{Barber\'{a}, P.}, Mayoral, J.A. \& Montero, J.R. ``\href{http://www.cepc.gob.es/publicaciones/revistas/revistaselectronicas?IDR=3&IDN=1360&IDA=37721}{Local Elections in Spain: A Multilevel Analysis of the Individual and Contextual Determinants of Voting}'', \textit{Revista de Estudios Pol\'{i}ticos}, 2016, 172, 47--82.

\item[9.] Fern\'{a}ndez-V\'{a}zquez, P., \textbf{Barber\'{a}, P.} \& Rivero, G. \href{http://dx.doi.org/10.1017/psrm.2015.8}{``Rooting out corruption or rooting for corruption? The Heterogenous Electoral Consequences of Scandals''}, \textit{Political Science Research and Methods}, 2016, 4 (2), 379--397.

\item[8.] \textbf{Barber\'{a}, P.}, Jost, J., Nagler, J., Tucker, J. \& Bonneau, R. ``\href{http://pss.sagepub.com/content/early/2015/08/21/0956797615594620}{Tweeting from Left to Right: Is Online Political Communication More Than an Echo Chamber?}'', \textit{Psychological Science}, 2015, 26 (10), 1531--1542.
\begin{itemize}
\item[] $\ast$ Methodology implemented to estimate political page affinity of Facebook users as part of the \href{https://socialscience.one/files/partnershipone/files/urls-v2_1.pdf}{Facebook Privacy-Protected Full URLs Data Set}, \href{https://socialscience.one/}{Social Science One}.
\end{itemize}

\item[7.] \textbf{Barber\'{a}, P.} \href{http://pan.oxfordjournals.org/cgi/reprint/mpu011?ijkey=uMFPw4dsMHM7608&keytype=ref}{``Birds of the Same Feather Tweet Together. Bayesian Ideal Point Estimation Using Twitter Data''}. \emph{Political Analysis}, 2015, 23 (1), 76--91.
\begin{itemize}
\item[] $\ast$ 2015 \href{http://oxfordjournals.org/our_journals/polana/editorschoice.html}{Editors' Choice article Award} for an article published in \textit{Political Analysis} that represents a ``especially significant contribution to political methodology.''
\vspace{-.1cm}
\item[] $\ast$ 2016 \href{http://www.apsanet.org/section-18-best-information-technology-and-politicsp-award}{Best Information Technology \& Politics Article Award}, given for the best published article about information technology and politics in 2015.
\vspace{-.1cm}
\item[] $\ast$ 2016 \href{http://www.oxfordjournals.org/our_journals/polana/awards_warrenmiller.html}{Warren Miller Article Award}, given by the Society of Political Methodology for the best article published in Political Analysis in 2015.
\vspace{-.1cm}
\item[] $\ast$ Featured in \textit{Political Analysis} virtual issue on \href{https://www.cambridge.org/core/journals/political-analysis/issue/online-research-methods/FF4E7D31B561F7FC794AF5894A53E9F3}{Innovative Methods in Online Research}
\end{itemize}


\item[6.] \textbf{Barber\'{a}, P.}, Wang, N., Bonneau, R., Jost, J., Nagler, J., Tucker, J. \& Gonz\'{a}lez-Bail\'{o}n, S. ``\href{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0143611}{The Critical Periphery in the Growth of Social Protests}", \textit{PLOS ONE}, 2015, 10 (11).

\item[5.] Vaccari, C., Valeriani, A., \textbf{Barber\'{a}, P.}, Bonneau, R., Jost, J., Nagler, J., Tucker, J. \href{http://onlinelibrary.wiley.com/doi/10.1111/jcc4.12108/abstract#.VLRLl9mdVFM.twitter}{``Political Expression and Action on Social Media: Exploring the Relationship Between Lower- and Higher-Threshold Political Activities Among Twitter Users in Italy''}, \emph{Journal of Computer-Mediated Communication}, 2015, 20 (2), 221--239.

\newpage 

\item[4.] \textbf{Barber\'{a}, P.} \& Rivero, G. \href{http://ssc.sagepub.com/content/33/6/712}{``Understanding the Political Representativeness of Twitter Users''}, \textit{Social Science Computer Review}, 2015, 33 (6), 721-729.

\item[3.] Vaccari, C., Valeriani, A., \textbf{Barber\'{a}, P.}, Bonneau, R., Jost, J., Nagler, J., Tucker, J. \href{http://www.rivisteweb.it/doi/10.1426/75245}{``Social Media and Political Communication. A survey of Twitter users during the 2013 Italian general election''}, \emph{Italian Political Science Review}, 2013, 43 (3), 381--410.

\item[2.] Riera, P., \textbf{Barber\'{a}, P.}, G\'{o}mez, R., Mayoral, J.A. \& Montero, J.R \href{http://link.springer.com/article/10.1007/s10611-013-9479-1}{``The Electoral Consequences of Corruption Scandals in Spain''}, \emph{Crime, Law and Social Change}, 2013, 60 (5), 515--534.

\item[1.] \textbf{Barber\'{a}, P} \href{http://www.reis.cis.es/REIS/PDF/REIS_132_021285919804928.pdf}{``Voting for Parties or for Candidates? The Trade-Off Between Party and Personal Representation in Spanish Regional and Local Elections''}, \emph{Revista Espa\~{n}ola de Investigaciones Sociol\'{o}gicas}, 2010, 132: 35--63.

\end{itemize}    

%__________________________________________________________________________________________________________________


\section{\mysidestyle Book\\Chapters} 
\vspace{.15cm}    
\begin{itemize}[leftmargin=5.5mm]
\item[6.] \textbf{Barber\'{a}, P.} 2020. \href{http://www.pablobarbera.com/static/echo-chambers.pdf}{``Social Media, Echo Chambers, and Political Polarization''}. \textit{Social Media and Democracy: The State of the Field}, edited by Nate Persily and Joshua Tucker. Cambridge University Press, pp. 34--55.

\item[5.] \textbf{Barber\'{a}, P.} \& Steinert-Threlkeld, Z. \href{http://www.pablobarbera.com/static/social-media-data-generators.pdf}{``How to Use Social Media Data for Political Science Research.'' } 2020. \textit{Sage Handbook of Research Methods in Political Science and International Relations}, edited by Robert Franzese and Luigi Curini. Sage, pp. 404--423.

\item[4.] Klasnja, M., \textbf{Barber\'{a}, P.}, Beauchamp, N., Nagler, J. \& Tucker, J. \href{http://www.oxfordhandbooks.com/view/10.1093/oxfordhb/9780190213299.001.0001/oxfordhb-9780190213299-e-3}{``Measuring Public Opinion with Social Media Data.''} 2018. \textit{The Oxford Handbook of Polling and Polling Methods}, edited by M. Alvarez. Oxford University Press, pp. 555--582.

\item[3.] \textbf{Barber\'{a}, P.}, \href{https://www.practicereproducibleresearch.org/case-studies/barbera.html}{``The Trade-Off Between Reproducibility and Privacy in the Use of Social Media Data to Study Political Behavior''} 2018. \textit{The Practice of Reproducible Research}, edited by Justin Kitzes. University of California Press, pp. 103--108. 

\item[2.] \textbf{Barber\'{a}, P.}, Vaccari, A. \& Valeriani, A. \href{https://link.springer.com/chapter/10.1057/978-1-137-59890-5_2}{``Social Media, Personalisation of News Reporting, and Media Systems' Polarisation in Europe''}. 2017. \textit{Social media and European politics: Rethinking power and legitimacy in the digital era}, edited by M. Barisione and A. Michailidou. Palgrave Macmillan, pp. 25--52

\item[1.] Tucker, J., Nagler, J., Metzger, M., \textbf{Barber\'{a}, P.}, Penfold-Brown, D. \& Bonneau, R. ``Big Data, Social Media, and Protest: Foundations for a Research Agenda''. 2016. \textit{Computational Social Science. Discovery and Prediction}, edited by R. Michael Alvarez. Cambridge University Press, pp. 199--204.
\end{itemize}
     %__________________________________________________________________________________________________________________


\section{\mysidestyle Other\\Publications}
    \vspace{.15cm}    
\begin{itemize}[leftmargin=5.5mm]
\item[4.] \textbf{Barber\'{a}, P.} ``\href{https://revista.cortesgenerales.es/rcg/article/view/1486}{Internet y Pol\'{i}tica: Consecuencias Pol\'{i}ticas y Sociales de la Revoluci\'{o}n Digital}'', \textit{Revista de las Cortes Generales}, 2020, 108 (1): 223--243.

\item[3.]  \textbf{Barber\'{a}, P.} \href{http://comparativenewsletter.com/files/archived_newsletters/2018_fall.pdf}{``Explaining the Spread of Misinformation on Social Media: Evidence from the 2016 U.S. Presidential Election''}, APSA \textit{Comparative Politics Newsletter}, 2018, 28 (2): 7--11.

\item[2.]  Tucker, J., Guess, A., \textbf{Barber\'{a}, P.}, Vaccari, C., Siegel, A., Sanovich, S., Stukal, D. \& Nyhan, B. \href{https://www.hewlett.org/library/social-media-political-polarization-political-disinformation-review-scientific-literature/}{``Social Media, Political Polarization, and Political Disinformation: A Review of the Scientific Literature''}, Report prepared for the \textit{Hewlett Foundation}, 2018.   

\item[1.]  Tucker, J., Theocharis, Y., Roberts, M. \& \textbf{Barber\'{a}, P.} \href{https://muse.jhu.edu/article/671987/pdf}{``From Liberation to Turmoil: Social Media and Democracy''}, \textit{Journal of Democracy}, 2017, 28 (4), 46-59.   
\end{itemize}     
    
%    \section{\mysidestyle Under\\Review} 

    % Work in progress
    \section{\mysidestyle Papers \\ Under Review} 


\textbf{Barber\'{a}, P.}, Iakhnis, E., Gohdes, A. \& Zeitzoff, T. ``Distract and divert: How world leaders use social media during contentious politics,'' \textit{under review}.

\newpage   

Timm, J. \& \textbf{Barber\'{a}, P.} ``Incivility Begets Incivility? Understanding the Contagion Dynamics of Uncivil Conversations on Social Media,'' \textit{under review}.

Guess, A., \textbf{Barber\'{a}, P.}, Munzert, S. \& Yang, J. ``The consequences of online partisan media,'' \textit{under review}

    \section{\mysidestyle Working\\Papers} 

\textbf{Barber\'{a}, P.} \href{http://www.pablobarbera.com/static/barbera_polarization_APSA.pdf}{``How Social Media Reduces Mass Political Polarization. Evidence from Germany, Spain, and the United States.''} 
\begin{itemize}
\item[] $\ast$ 2016 \href{http://www.apsanet.org/PROGRAMS/APSA-Awards/Franklin-L-Burdette-Pi-Sigma-Alpha-Award}{Franklin L. Burdette/Pi Sigma Alpha Award} for Best Paper Presented at APSA 2015.
\end{itemize}  

\textbf{Barber\'{a}, P.} \href{http://pablobarbera.com/static/less-is-more.pdf}{``Less is More? How Demographic Sample Weights can Improve Public Opinion Estimates Based on Twitter Data.''}

%``Tweeting to the choir? Measuring exposure to ideologically diverse campaign messages on Twitter.'' (with Joshua Timm and Javier Lorenzo)

Hua, W., Abou-Chadi, T. \& \textbf{Barber\'{a}, P.} ``Networked Populism: Characterizing the Public Rhetoric of
Populist Parties in Europe.''





% \section{\mysidestyle Book\\Chapters\\Under Review} 
%__________________________________________________________________________________________________________________
    % Grants

        \section{\mysidestyle External \\ Grants}
        
\textit{How online incivility affects the interactions between public officials and citizens on Facebook,} \$35,000. Facebook Research Faculty Grant. 2018.        
        
\textit{Paying Attention to Attention: Media Exposure and Opinion Formation in an Age of Information Overload,} 736,600\euro. Volkswagen Foundation. Co-principal investigator, with Simon Munzert, Andrew Guess, JungHwan Yang. 2017.

    \textit{Electoral Behavior in Spanish Local Elections: A Multilevel Approach,} 10,000\euro. Spanish Center for Sociological Research (CIS). Co-principal investigator, with Jos\'{e} Ram\'{o}n Montero, Pedro Riera, Ra\'{u}l G\'{o}mez, and Juan A. Mayoral. 2011.    

 %__________________________________________________________________________________________________________________
    % Grants

        \section{\mysidestyle Internal\\Grants}

Center for International Studies, University of Southern California:
\begin{itemize}
\item[] Faculty Research Grant, \$5,000. 2016
\vspace{-.15cm}
\item[] Research Assistantship Grant, \$22,000. 2017
\vspace{-.15cm}
\item[] Conference support, \$15,000. 2017
\end{itemize}
Dornsife College of Letters, Arts and Sciences, University of Southern California:
\begin{itemize}
\item[] Student Opportunities for Academic Research Program, \$3,000. 2016--2017.
\vspace{-.15cm}
\item[] Undergraduate Research Associates Program, \$4,500. 2017--2018.
\end{itemize}
 
    %__________________________________________________________________________________________________________________
    % Fellowships and Awards


    \section{\mysidestyle Fellowships\\ and Awards}
	Warren Miller Prize, Society for Political Methodology, 2016.\nl
    Franklin L. Burdette/Pi Sigma Alpha Award, American Political Science Association, 2016.\nl
	``La Caixa'' Fellowship for Graduate Studies in the U.S., 2010-2012. \nl
	``Salvador de Madariaga'' Fellowship, European University Institute, 2009-2010. \nl
	 2nd National Prize to Excellence in Academic Performance, 2008. \nl
	Pompeu Fabra University graduation prize for Exceptional Achievement, 2008.

\newpage
            \section{\mysidestyle Teaching}

\emph{Instructor}
\begin{itemize}
\item Spring 2017, Fall 2020: Introduction to Regression Analysis (USC POIR 611)
\item Fall 2017, 2019: \href{http://pablobarbera.com/POIR613/}{Computational Social Science} (USC POIR 613)
\item Lent 2019: \href{https://lse-my459.github.io/}{Quantitative Text Analysis} (LSE MY 459)
\item Michaelmas 2018: \href{https://lse-my472.github.io/}{Data for Data Scientists} (LSE MY 472, co-taught with Akitaka Matsuo)
\item Lent 2018: \href{https://lse-my459.github.io/}{Quantitative Text Analysis} (LSE MY 459, co-taught with Ken Benoit)
\item Fall 2017: International Relations -- Approaches to Research (USC IR 211)
\item Fall 2016: Introduction to Data Analysis (USC IR 312)
\item Fall 2016: European Integration (USC IR 468)
\end{itemize}



\emph{Workshops \& Summer Schools}
\begin{itemize}
\item \href{https://www.lse.ac.uk/study-at-lse/executive-education/courses/secure/business-and-management/data-science-for-decision-making}{Data Science for Decision-Making} (10 hours), Executive Education Course, London School of Economics (co-taught with Ken Benoit), 2018
\item \href{http://pablobarbera.com/SQL-workshop/}{Querying large-scale online datasets: SQL and Google BigQuery} (4 hours). London School of Economics, 2018.
\item \href{http://pablobarbera.com/text-analysis-vienna/}{Quantitative Text Analysis with Applications to Social Media Research} (20 hours) University of Vienna, 2018
\item \href{https://ecpr.eu/Events/PanelDetails.aspx?PanelID=7061&EventID=116}{Big Data Analysis in the Social Sciences} (15 hours) ECPR Summer School, Central European University (2017, 2018)
\item \href{https://ecpr.eu/Events/PanelDetails.aspx?PanelID=7055&EventID=116}{Automated Collection of Web and Social Data} (15 hours) ECPR Summer School, Central European University. (2017, 2018)
\item \href{https://github.com/pablobarbera/eui-text-workshop}{Automated Text Analysis with R} (6 hours) Quantitative Methods Working Group, European University Institute, 2016
\item \href{https://github.com/pablobarbera/data-science-workshop}{Data Science and Social Science} (18 hours) Center for the Promotion of Research Involving Innovative Statistical Methodology (PRIISM), New York University, 2016. (Joint with Alex Hanna and Dan Cervone)
\item \href{http://pablobarbera.com/eitm}{Social Media and Big Data Research} (12-15 hours)
\begin{itemize}
\vspace{-.1cm}
\item Summer School in Survey Methodology, Pompeu Fabra University, 2017, 2018.
\vspace{-.1cm}
\item EITM Europe Summer Institute, 2018.
\end{itemize}
\item \href{http://pablobarbera.com/social-media-workshop/}{Collecting and Analyzing Social Media Data with R} (2--4 hours)
\begin{itemize}
\vspace{-.1cm}
\item Georgetown University, 2015
\vspace{-.1cm}
\item University of Cologne, 2017
\vspace{-.1cm}
\item London School of Economics, 2018
\end{itemize}
\item \href{https://github.com/pablobarbera/workshop}{Scraping Twitter \& Web Data} and \href{https://github.com/pablobarbera/Rdataviz}{Data Visualization with ggplot2} (4 hours) NYU Politics, 2013.
\end{itemize}

\emph{Project Advisor}
\begin{itemize}
\item Fall 2015: \href{http://cds.nyu.edu/academics/ms-in-data-science/curriculum/required-courses/#ds-ga-1006}{Capstone Project in Data Science}, MS in Data Science
\end{itemize}

\emph{Member of dissertation committees:} Adam Badawy (USC), Whitney Hua (USC), Fridolin Linder (Penn State), Xinru Ma (USC), Marius S\"{a}ltzer (Mannheim), Philipp Kling (Konstanz), Joshua Timm (USC), Joe Hoover (USC), Nicol\'{a}s Albertoni (USC), Timo Daehler (USC), Nicholas Napolio (USC), Anuja Majmundar (USC).


%\emph{Teaching Assistant}
%\begin{itemize}
%\item January 2014 \& 2015: \href{https://github.com/pablobarbera/NYU-AD-160J}{Social Media and Political Participation} (undergraduate), Joshua Tucker.
%\item Fall 2013: \href{https://github.com/pablobarbera/quant3materials}{Quantitative Methods III} (PhD), Neal Beck
%\item Fall 2012, Spring 2013: IR Senior Honors Seminar (undergraduate), Michael Gilligan
%\end{itemize}

%__________________________________________________________________________________________________________________
    % Invited talks

        \section{\mysidestyle Invited\\talks}
2020:
\begin{itemize}
\item California Center for Population Research Seminar (UCLA)
\item Polarization and Social Change Lab (Stanford University)
\item Free Speech, Democracy, and the Internet (Stanford University)
\item MIT Media Lab
\item Weekly Workshop in Political Science (Leiden University)
\end{itemize}    
    
2019: 
\begin{itemize} 
\item Politics Research Colloquium (University of Oxford).
\item Instituto Carlos III - Juan March Permanent Seminar (Universidad Carlos III)
\item Summer Institute in Computational Social Science (University of Oxford)
\end{itemize}
2018: 
\begin{itemize} 
\item Political Science Departmental Research Seminar (UCL -- University College London)
\item Project on Democracy and the Internet Seminar Series (Stanford University)
\item Reuters Institute for the Study of Journalism (Oxford University)
\item Institute of Social Sciences (University of Lisbon)
\item Sage Ocean Speaker Series (Sage)
\item Paul Lazarsfeld Guest Professor (University of Vienna)
\item Department of Government Seminar Series (University of Essex)
\item International Methods Colloquium (Wake Forest University)

\item Q-Step Seminar Series (University of Exeter).
\end{itemize}
2017:    
\begin{itemize}
\item Symposium on Computational Social Science (Chair of Systems Design, ETH Z\"{u}rich)
\item Center for Public Diplomacy (University of Southern California)
\item Seminario sobre Pol\'{i}tica, Redes Sociales y Big Data (Universidad Central de Chile)
\item Department of Methodology (London School of Economics)
\item Methods Speaker Series (UCSD)
\item Comparative Political Behavior Lecture Series (Humboldt University, Berlin)
\item Research Seminar in American Politics (UC Berkeley)
\item Lecture Series -- Microfoundations of Politics (University of Cologne).
\end{itemize}
2016:
\begin{itemize}
\item Center for Statistics and the Social Sciences (University of Washington)
\item Department of Political Science Seminar Series (University of Copenhagen)
\item International Political Communication Workshop (Universit\'{e} Laval)
\item Artificial Intelligence Seminar (Information Sciences Institute, USC).
\item Social Media, Methods, and Politics Seminar (Universit\`{a} degli studi di Milano)
\end{itemize}
2015:
\begin{itemize}
\item Digital Media, Networks, and Political Communication research group (Annenberg School of Communication, UPenn)
\item Microsoft Research Seminar Series (Microsoft Research, New York)
\end{itemize}

\newpage     
  
        \section{\mysidestyle Workshop\\Participation}
2020: Social Science Foo Camp (O'Reilly and Facebook), Annual Conference of the Center for Social Media and Politics (NYU), Summer Institute in Computational Social Sciences (Duke University), Conference on Politics and Computational Social Science (Northeastern University), NSF Workshop on Social Media Data Acquisition and Sampling (University of Michigan and Georgetown University).
        
2019: Workshop on Text Analysis for Asia and Beyond (University of Southern California), Economics of Media Bias Workshop (WZB -- Berlin Social Science Center), Causes and Consequences of Populism (London School of Economics), Workshop: Center for Social Media and Politics (New York University).
    
      
2018: Social Science Foo Camp (O'Reilly and Facebook), International Workshop on Social Media and Political Participation (SMaPP Global, NYU Shanghai), Academic Workshop on Social Media and Misinformation (Facebook \& Harvard University), Workshop: Is there room in National Election Studies for Big Data? (University of Manchester), Symposium: The Consequences of Misinformation (Brookings Institution and Social Science Research Council), Workshop: Political Economy in the Digital Age (Hertie School of Governance).



2017: International Workshop on Social Media and Political Participation (SMaPP Global, NYU Abu Dhabi), Workshop: Navigating bots, algorithms, echo chambers, and disinformation (U.S. State Department \& Stanford University), Workshop: The Future of Humans as Sensors for Social Science Research (UCLA),  International Workshop on Social Media and Political Participation (SMaPP Global, NYU), Academic Workshop on Social Media and Political Polarization (Facebook \& Stanford University).

2016: International Workshop on Social Media and Political Participation (SMaPP Global), Text Analysis Conference (University of Amsterdam).

2015: Conference on Political Polarization: Media and Communication Influences (Princeton University, CSDP), Big Data and Political Science Conference (University of Mannheim), Workshop on Online Politics (University College Dublin), International Workshop on Social Media and Political Participation (SMaPP Global)

        \section{\mysidestyle Conference\\Presentations}
        
2020: APSA. 2019: APSA, EPSA. 2018: EPSA, MPSA; 2017: APSA, EPSA, ISA, MPSA; 2016: APSA, EPSA, PolMeth, ISA, MPSA; 2015: APSA, EPSA, PolMeth, MPSA


\section{\mysidestyle Professional\\Memberships}

\emph{Member:} American Political Science Association (Political Methodology, Political Networks, and Information Technology \& Politics sections), European Political Science Association.


   
%__________________________________________________________________________________________________________________
    %Other work experience
%                \section{\mysidestyle Other work\\experience}
%    Research Assistant to Professor Jonathan Nagler (NYU), 2012, 2014, 2015\nl
%    Research Assistant, Social Media and Political Participation (SMaPP) Lab, 2013--2015
    
%__________________________________________________________________________________________________________________
    %Skills
%            \section{\mysidestyle Skills}
    
%\emph{Software}

%\begin{itemize}
%\item Advanced: R, JAGS, stan, Stata, \LaTeX 
%\item Intermediate: Python, SPSS, mySQL, Gephi, Netlogo, mongoDB
%\item Code repository: \href{http://www.github.com/pablobarbera}{github.com/pablobarbera}
%\end{itemize}\vspace{-.5cm}
%\emph{Languages}\nl
%\indent Spanish (native), Catalan (fluent), English (fluent)
    
   
%__________________________________________________________________________________________________________________
    %Teaching
    


%__________________________________________________________________________________________________________________
    %Other work experience
\section{\mysidestyle Professional\\Service}

\emph{Journal editor}: SAGE Open, \href{https://journals.sagepub.com/topic/sgo-subjects/3468/sgo}{special issue on "Social Media and Politics"}.\nl
\emph{Editorial Board}: \href{https://www.cambridge.org/core/journals/political-analysis/information/editorial-board}{Political Analysis}, \href{https://www.journals.uchicago.edu/journals/jop/board}{Journal of Politics}.\nl
\emph{Advisory Board}: \href{https://www.pewresearch.org/methods/about-data-labs/}{Pew Research Center Data Labs}.\nl
\emph{Referee}: over 100 reviews for more than 40 different journals or conferences, including American Political Science Review, Proceedings of the National Academy of Sciences, American Journal of Political Science, The Journal of Politics, Political Analysis, British Journal of Political Science, Political Communication, Journal of Communication, ICWSM, WWW, Oxford University Press, National Science Foundation, Austrian Science Fund. For full list, \textbf{see my \href{https://publons.com/author/1291880/pablo-barbera}{Publons profile}}.\nl
% \textbf{(see also \href{https://publons.com/author/1291880/pablo-barbera}{Publons profile})} American Political Science Review (x2), Proceedings of the National Academy of Sciences, American Journal of Political Science (x2), The Journal of Politics (x3), Political Analysis (x3), British Journal of Political Science, Party Politics, Political Studies (x2), Political Science Research and Methods (x2), Research \& Politics (x2) Policy and Internet, ICWSM, Public Opinion Quarterly (x2), Political Communication (x7), Political Research Quarterly, New Media \& Society, Social Science Computer Review (x4), Social Networks, Social Media + Society, Economics \& Politics, American Journal of Sociology, Psychological Science, Journal of Elections, Public Opinion \& Parties (x2); Journal of Communication, Regional \& Federal Studies, Journal of Law and Courts, Kyklos, Wiley, Russell Sage Foundation, South European Society and Politics, Revista Espa\~{n}ola de Investigaciones Sociol\'{o}gicas, Revista Espa\~{n}ola de Ciencia Pol\'{i}tica, MIS Quarterly, Information, Communication, and Society, Communication Methods and Measures, International Journal of Communication, EPJ Data Science.\nl
\emph{Conferences}: chair (EPSA 2013, 2014, 2016, 2017, 2018; MPSA 2016, 2017, 2018; APSA 2017), discussant (EPSA 2014, 2015; APSA 2015, 2017; MPSA 2016, 2017, 2018).
\newpage
\emph{Service in Conference Program Committees}: European Political Science Association Conference (2014), SocInfo: Social Informatics (2016), ICWSM: International Conference on Weblogs and Social Media (2017), IC2S2: International Conference on Computational Social Science (2017, 2019), General Online Research Conference (2018),  International World Wide Web Conference -- WWW (2018, 2019), ACM Web Science Conference (2019).\nl
\emph{Service in Award Committees}: chair of APSA Political Networks section Political Ties award committee (2016), chair of APSA Information Technology and Politics section best paper award committee (2017), member of Miller Prize Award committee (2017, 2018), member of ICA Computational Methods interest group best paper award committee (2018), member of APSA Information Technology and Politics section best conference paper award committee (2018), member of PolMeth best poster award committee (2019), member of APSA Information Technology and Politics section best dissertation award committee (2020).

                \section{\mysidestyle University\\Service}
                
\emph{Admin}: 
\begin{itemize}
\item Methods Field co-developer, POIR PhD program, USC 2016--2017.
\item Methods Field advisor, POIR PhD program, USC 2016--present.
\item Programme Director, MSc in Applied Social Data Science, LSE 2018--2019.
\end{itemize}
\emph{Organizer}: 
\begin{itemize}
\item Networked Democracy Lab Speaker Series (USC, Fall \& Spring 2017).
\item Workshop on Media Exposure and Opinion Formation (USC, Fall 2017).
\item Social Data Science Professionalization Seminar (LSE, 2018).
\end{itemize}





%__________________________________________________________________________________________________________________
    % Software
    
        \section{\mysidestyle Software}
    
\href{http://cran.r-project.org/web/packages/streamR/}{streamR}: Access to Twitter Streaming API via R. Available on CRAN. 113K total downloads. \nl
\href{http://cran.r-project.org/web/packages/Rfacebook/index.html}{Rfacebook}: Access to Facebook API via R. Available on CRAN. 137K total downloads.\nl
\href{http://cran.r-project.org/web/packages/instaR/index.html}{instaR}: Access to Instagram API via R. Available on CRAN. 26K total downloads. \nl
\href{http://www.tweetscores.com}{tweetscores}: R tools for analysis of Twitter data. Includes functions to estimate ideology of Twitter users.


%__________________________________________________________________________________________________________________
    %Media
                \section{\mysidestyle Writings in Popular Media}
``\href{https://www.washingtonpost.com/news/monkey-cage/wp/2017/12/06/this-explains-how-social-media-can-both-weaken-and-strengthen-democracy/?utm_term=.d52c930452e9}{This explains how social media can both weaken -- and strengthen -- democracy},'' with Joshua Tucker, Yannis Theocharis, and Margaret E. Roberts. Published in The Monkey Cage / Washington Post, 2017.\nl               
``\href{https://www.washingtonpost.com/news/monkey-cage/wp/2016/11/04/twitter-trolls-hurt-democracy-more-than-you-realize-heres-how/}{Twitter trolls are actually hurting democracy},'' with Yannis Theocharis, Zoltan Fazekas, and Sebastian Popa. Published in The Monkey Cage / Washington Post, 2016.\nl
``\href{https://www.washingtonpost.com/news/monkey-cage/wp/2015/11/30/why-everyone-in-a-network-is-important-for-movements-even-the-slactivists/}{Why everyone in a network is important for movements -- even the Slacktivists!},'' with Sandra Gonz\'{a}lez-Bail\'{o}n. Published in The Monkey Cage / Washington Post, 2015.\nl
``\href{http://www.washingtonpost.com/blogs/monkey-cage/wp/2015/06/16/who-is-the-most-conservative-republican-candidate-for-president/}{Who is the most conservative Republican candidate for president?}.'' Published in The Monkey Cage / Washington Post, 2015.\nl
``\href{http://blogs.lse.ac.uk/politicsandpolicy/political-discussions-on-twitter-during-elections-are-dominated-by-those-with-extreme-views/}{Political discussions on Twitter during elections are dominated by those with extreme views},'' with Gonzalo Rivero. European Politics and Policy (EUROPP) Blog, London School of Economics.\nl
 ``\href{http://www.huffingtonpost.com/pablo-barbera/tweeting-the-revolution-s_b_4831104.html}{Tweeting the Revolution: Social Media Use and the \#Euromaidan Protests},'' with Megan Metzger. Published on The Huffington Post, 2014.\nl
 ``\href{http://www.washingtonpost.com/blogs/monkey-cage/wp/2013/12/04/strategic-use-of-facebook-and-twitter-in-ukrainian-protests/}{How Ukrainian protestors are using Twitter and Facebook},'' with Megan Metzger. Published in The Monkey Cage / Washington Post, 2014.\nl
 ``\href{http://themonkeycage.org/2013/06/01/a-breakout-role-for-twitter-extensive-use-of-social-media-in-the-absence-of-traditional-media-by-turks-in-turkish-in-taksim-square-protests/}{A Breakout Role for Twitter? The Role of Social Media in the Turkish Protests},'' with Megan Metzger. Published in The Monkey Cage / Washington Post, 2013.\nl
 ``\href{http://themonkeycage.org/2013/06/30822/}{The Dynamics of Information Diffusion in the Turkish Protests},'' with Sandra Gonz\'{a}lez-Bail\'{o}n. Published in The Monkey Cage / Washington Post, 2013.\nl
\href{http://www.tuitometro.es}{tuitometro.es}, Real-time tracking of the Spanish 2011 legislative election in Twitter using automatized sentiment analysis, with Gonzalo Rivero (NYU). Featured in the major Spanish newspapers.
  

                \section{\mysidestyle Mentions in Media Outlets}
The Atlantic, ``\href{https://www.theatlantic.com/ideas/archive/2019/04/political-leaders-should-stop-caring-about-twitter/588004/}{The Problem Isn't Twitter. It's That You Care About Twitter},'' April 29, 2019.\nl
El Pa\'{i}s, ``\href{https://elpais.com/tecnologia/2019/01/09/actualidad/1547029983_955487.html}{?`Enga\~{n}an las noticias falsas sobre todo a los m\'{a}s mayores?},'' Jan 9, 2019.\nl
C-SPAN, ``\href{https://www.c-span.org/video/?446330-3/social-media-false-information-panel-2}{Social Media and False Information Panel, Brookings Institution},'' May 31, 2018.\nl                
Vox, ``\href{http://www.vox.com/the-big-idea/2016/12/28/14095452/fake-news-political-bubbles-democracy-facebook}{Fake news aside, Facebook can help puncture our political bubbles},'' Dec 28, 2016.\nl
El Pa\'{i}s, ``\href{http://internacional.elpais.com/internacional/2016/11/25/actualidad/1480095728_565471.html}{As\'{i} influye Facebook en tus opiniones. Las noticias falsas circulan m\'{a}s r\'{a}pido en c\'{a}maras de eco},'' Nov 27, 2016.\nl
Los Angeles Times, ``\href{http://www.latimes.com/politics/la-na-pol-trump-twitter-20161122-story.html}{Trump's Twitterfests are meant to further the culture wars that helped win him the presidency},'' Nov 22, 2016.\nl 
The Economist, ``\href{http://www.economist.com/news/special-report/21695192-social-media-now-play-key-role-collective-action-new-kind-weather}{A new kind of weather},'' Mar 26, 2016.\nl
WIRED, ``\href{http://www.wired.com/2015/12/social-media-is-making-the-debate-on-guns-and-trump-worse/}{Social media is making the debate on guns -- and Trump -- worse},'' Dec 16, 2015.\nl
Quartz, ``\href{http://qz.com/570009/slacktivism-is-having-a-powerful-real-world-impact-new-research-shows/}{Slacktivism is having a powerful real-world impact, new research shows},'' Dec 10, 2015\nl
Vox, ``\href{http://www.vox.com/2015/12/8/9873822/social-media-activism-science}{Changing your Facebook profile picture is doing more good than you might think},'' Dec 8, 2015\nl
Pacific Standard, ``\href{https://psmag.com/the-upside-of-slacktivism-2a93294941b0#.hp2xyepdf}{The Upside of Slacktivism},'' Dec 3, 2015\nl
New York Times, ``\href{http://www.nytimes.com/2014/11/21/upshot/social-media-deepens-partisan-divides-but-not-always.html?_r=0}{Social Media Deepens Partisan Divides. But Not Always.},'' Nov 20, 2014.\nl
New York Times, ``\href{http://www.nytimes.com/2014/10/25/upshot/americans-dont-live-in-information-cocoons.html?_r=0}{Americans Don't Live in Information Cocoons},'' Oct 24, 2014\nl
Wall Street Journal, ``\href{http://blogs.wsj.com/washwire/2014/10/21/study-social-media-can-moderate-users-politics/}{Study: Social Media Can Moderate Users' Politics},'' Oct 21, 2014\nl
Nieman Lab, ``\href{http://www.niemanlab.org/2014/10/this-study-finds-that-social-media-use-reduces-political-polarization-instead-of-increasing-it/}{This study finds that social media use reduces political polarization instead of increasing it},'' October 20, 2014\nl
The Atlantic, ``\href{http://www.theatlantic.com/international/archive/2013/06/these-charts-show-how-crucial-twitter-is-for-the-turkey-protesters/276798/}{These Charts Show How Crucial Twitter Is for the Turkey Protesters},'' Jun 12, 2013.\nl
Foreign Policy, ``\href{http://foreignpolicy.com/2013/06/03/is-facebook-a-town-square-or-a-shopping-mall/}{Is Facebook a town square or a shopping mall?},'' June 3, 2014.\nl

%\vspace{1cm}
\centering \textbf{Last updated: \today}
    
\end{resume}
\end{document}
%______________________________________________________________________________________________________________________
% EOF